### 2024-02-21 documentation/thesis/thesis_document.tex
final

\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{1000ppm from 50mT needed resolution calucation I}

@@

\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{1000ppm from 50mT needed resolution calucation II}

@@

\noteworthy{\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}}{Center of Gravity}

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(N_{baseline}\) & 10000 & 10000 & - & Samples measured for
baseline\tabularnewline
\(N_{measurement}\) & 2000 & 2000 & - & Samples measured for
measurement\tabularnewline
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Sensor
temperature coefficients\tabularnewline
DR & {[}-138;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
\gls{dr}\tabularnewline
\bottomrule
\end{longtable}

>>>>

\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{: 1000ppm from 50mT needed resolution calucation I}

@@

\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{: 1000ppm from 50mT needed resolution calucation II}

@@

\noteworthy{\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}}{: Center of Gravity}

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(N_{baseline}\) & 10000 & 10000 & - & Samples measured for
baseline\tabularnewline
\(N_{measurement}\) & 2000 & 2000 & - & Samples measured for
measurement\tabularnewline
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Sensor
temperature coefficients\tabularnewline
DR & {[}-178;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
\gls{dr}\tabularnewline
\bottomrule
\end{longtable}
